---
title: "Homework 1"
author: Amanda Warnock
output: github_document
---

This is my solution to HW1.

```{r pull_library}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r create_df}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```

Take the mean of each variable in my data frame. 

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical, but not character or factor. 

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

I can convert the sample numbers and logical vector to numeric, which is why the mean worked. I cannot convert the character vector, which is why it didn't work. I can convert the factor vector, but not in a way that is meaningful yet. 

Below, I convert the logical vector to numeric and multiply the random sample by the result. 
```{r mult_1}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```

Below, I convert the logical vector to a factor and multiply the random sample by the result. This does not work.

```{r mult_2}
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```

Below, I convert the logical vector to a factor and then convert the result to numeric, and then multiply the random sample by the result. This now works. 

```{r mult_3}
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```


## Problem 2

I have installed the package containing penguins dataset. 
I will now load the penguins dataset.

```{r penguins, echo = FALSE}
data("penguins", package = "palmerpenguins")
```

Some important variables in this dataset include `r names(penguins)`. The penguin datset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
The mean bill length is `r round(mean(penguins$bill_length_mm, na.rm = TRUE), 1)`mm and the mean bill depth is `r round(mean(penguins$bill_depth_mm, na.rm = TRUE), 1)`mm. The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 1)`mm. The mean body mass is `r round(mean(penguins$body_mass_g, na.rm = TRUE), 1)`g. 

The species included are `r unique(pull(penguins, species))`. The years included are `r unique(pull(penguins, year))`. The islands included are `r unique(pull(penguins, island))`. 


Below is a scatter plot comparing bill length (mm) and flipper length (mm).

```{r plot}
plot_df = tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm,
  species = penguins$species
)

ggplot(data = plot_df, 
       aes(x = x, 
           y = y, 
           color = species)) + geom_point() + 
      labs(title = "bill and flipper length", 
           x = "bill length (mm)", 
           y = "flipper length (mm)") 

ggsave(
  hw1_plot,
  plot = last_plot(),
  device = NULL,
  path = NULL,
  scale = 1, 
  limitsize = TRUE
)
```

